Extended Data

### 2021-11-18 doc/manuscript/Dow_manuscript_Nature.Rmd
improve wording

Both MODIS-derived canopy foliage phenology and dendrometer band measurements of stem growth phenology generally shifted backwards as spring temperatures increased (Fig. `r DOY_timing`, `r EDF_pheno_all`). 
We found a consistent effect of temperature ($T_{max}$ or $T_{min}$) throughout the spring, but the strongest effects on stem-growth phenology were found using $T_{max}$ during a critical temperatrue window (CTW). 
CTW was identified by measuring the correlation between all combinations of weekly $T_{max}$ and $DOY_{25}$ from January 1 and $DOY_{25}$ (`r EDF_climwin`).
The CTW was defined as the week(s) which had the strongest correlation with $DOY_{25}$.

>>>>

Both MODIS-derived canopy foliage phenology and dendrometer band measurements of stem growth phenology generally shifted backwards as spring temperatures increased (Fig. `r DOY_timing`, `r EDF_pheno_all`). 
We found a consistent effect of temperature ($T_{max}$ or $T_{min}$) throughout the spring, but the strongest effects on stem-growth phenology were found using $T_{max}$ during a critical temperatrue window (CTW). 
CTW was identified by measuring the correlation between all combinations of weekly $T_{max}$ and $DOY_{25}$ from January 1 to mean $DOY_{25}$ for each xylem porosity-site combination (`r EDF_climwin`).
The CTW was defined as the week(s) which had the strongest correlation with $DOY_{25}$.
